Proplyd distribution

### 2020-02-06 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
First look at thickness statistics - uncorrelated with shape 😒

%%% 2017-04-19 13:16:10.731012

@@

	\begin{tabular}{@{} ll @{\quad } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS[round-mode=places] @{\quad} S@{}S@{}S @{}}\toprule
	  & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\ 
	  {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)} & {(3)} & {(4)} & {(5)} & {(6)} & {(7)} & {(8)} & {(9)} & {(10)}  & {(11)} & {(12)} & {(13)} & {(14)} & {(15)} & {(16)} \\  
	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\

@@

Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
\(H\) magnitude & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\

@@

Low/high & \(R_{90}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & \itshape 0.428 & \bfseries 0.00139\\
bow shock size, \(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\

@@

Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
extinction, \(A_K\) & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\

@@

Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
\(\vert{}b\vert\) & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\

@@

High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
\(\cos \ell\) & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\

@@

\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\

@@

Environment: & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
Isolated vs Facing & \(\Delta R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\

@@

Environment: & \(R_{90}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
Isolated vs \hii & \(\Delta R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\

@@

Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\

@@

With/without & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\

@@

MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
 & \(\Delta R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\

@@

MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
 & \(\Delta R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505

>>>>

%%% 2020-02-05 22:21:40.747825

@@

	\begin{tabular}{
	  @{} ll @{\quad }
	  % Mean
	  S[round-mode=places]S[round-mode=places]
	  % Std Dev
	  S[round-mode=places]S[round-mode=places]
	  % Obs Disp
	  SS
	  % Effect sizes
	  @{\quad} SSS[round-mode=places]
	  % p values
	  @{\quad}
	  S[table-format = +1.2e1]
	  S[table-format = +1.2e1]
	  S[table-format = +1.2e1] @{}
	  }\toprule
	  & {Dependent}
	  & \multicolumn{2}{c}{Mean}
	  & \multicolumn{2}{c}{Std.\ Dev.}
	  & \multicolumn{2}{c}{Obs.\ Disp.}
	  & \multicolumn{3}{c @{} }{\dotfill Effect sizes\dotfill }
	  & \multicolumn{3}{c @{}}{Non-parametric test \(p\)-values} \\ 
	  {Comparison} & {Variable}
	  & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)}
	  & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)}
	  & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)}
	  & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)}
	  & {K--S} & {Rank} &  {B--F}\\
	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)}
	  & {(3)} & {(4)}
	  & {(5)} & {(6)}
	  & {(7)} & {(8)}
	  & {(9)} & {(10)} & {(11)}
	  & {(12)} & {(13)} & {(14)}  \\  
	  \midrule\multicolumn{10}{@{} l @{}}{\itshape Median split of continuous independent variables}\\

@@

Faint/bright & \(\Pi\) & 1.701 & 1.872 & 0.605 & 0.806 & 0.101 & 0.084 & 0.103 & 0.24 & 1.333 & 0.379 & 0.182 & 0.0588\\
\(H\) magnitude & \(\Lambda\) & 1.655 & 1.724 & 0.255 & 0.322 & 0.238 & 0.232 & 0.147 & 0.237 & 1.262 & \itshape 0.018 & 0.057 & 0.0884\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.176 & 0.196 & 0.152 & 0.155 &   &   & 0.087 & 0.13 & 1.019 & 0.921 & 0.261 & 0.833\\

@@

Low/high & \(\Pi\) & 1.696 & 1.874 & 0.668 & 0.75 & 0.115 & 0.07 & \itshape 0.171 & \itshape 0.251 & 1.123 & 0.431 & \itshape 0.0261 & 0.66\\
bow shock size, \(R_0\) & \(\Lambda\) & 1.67 & 1.71 & 0.266 & 0.314 & 0.251 & 0.22 & 0.103 & 0.135 & 1.18 & \itshape 0.0351 & 0.18 & 0.184\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.174 & 0.197 & 0.148 & 0.159 &   &   & 0.049 & 0.148 & 1.073 & 0.345 & 0.521 & 0.201\\

@@

Low/high & \(\Pi\) & 1.769 & 1.805 & 0.761 & 0.672 & 0.096 & 0.088 & 0.067 & 0.05 & 0.883 & 0.771 & 0.388 & 0.477\\
extinction, \(A_K\) & \(\Lambda\) & 1.681 & 1.697 & 0.269 & 0.314 & 0.234 & 0.236 & 0.021 & 0.055 & 1.168 & 0.771 & 0.789 & 0.415\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.189 & 0.184 & 0.139 & 0.168 &   &   & -0.069 & -0.032 & 1.207 & 0.572 & 0.373 & 0.306\\

@@

Low/high & \(\Pi\) & 1.769 & 1.804 & 0.713 & 0.719 & 0.089 & 0.095 & 0.01 & 0.049 & 1.009 & 0.974 & 0.896 & 0.771\\
\(\vert{}b\vert\) & \(\Lambda\) & 1.69 & 1.691 & 0.315 & 0.266 & 0.242 & 0.228 & 0.015 & 0.004 & 0.844 & 0.653 & 0.85 & 0.534\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.182 & 0.19 & 0.151 & 0.157 &   &   & 0.045 & 0.05 & 1.04 & 0.415 & 0.556 & 0.683\\

@@

High/low & \(\Pi\) & 1.797 & 1.771 & 0.714 & 0.719 & 0.094 & 0.089 & -0.027 & -0.035 & 1.007 & 0.724 & 0.728 & 0.999\\
\(\cos \ell\) & \(\Lambda\) & 1.7 & 1.676 & 0.284 & 0.302 & 0.236 & 0.234 & -0.021 & -0.081 & 1.063 & 0.973 & 0.792 & 0.937\\
\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(\Delta \Lambda\) & 0.174 & 0.204 & 0.146 & 0.164 &   &   & 0.088 & 0.197 & 1.124 & 0.871 & 0.262 & 0.327\\

@@

\multicolumn{10}{@{} l @{}}{\itshape Categorical independent variables}\\

@@

Environment: & \(\Pi\) & 1.802 & 1.784 & 0.705 & 0.738 & 0.093 & 0.085 & -0.035 & -0.026 & 1.046 & 0.259 & 0.727 & 0.671\\
Isolated vs Facing & \(\Lambda\) & 1.699 & 1.674 & 0.281 & 0.304 & 0.239 & 0.223 & -0.078 & -0.088 & 1.081 & 0.883 & 0.439 & 0.919\\
\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(\Delta \Lambda\) & 0.182 & 0.201 & 0.153 & 0.16 &   &   & 0.061 & 0.12 & 1.042 & 0.69 & 0.549 & 0.549\\

@@

Environment: & \(\Pi\) & 1.802 & 1.62 & 0.705 & 0.756 & 0.093 & 0.105 & -0.265 & -0.257 & 1.072 & \itshape 0.0201 & 0.0804 & 0.422\\
Isolated vs \hii & \(\Lambda\) & 1.699 & 1.636 & 0.281 & 0.36 & 0.239 & 0.22 & -0.224 & -0.216 & 1.279 & 0.11 & 0.14 & 0.0601\\
\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(\Delta \Lambda\) & 0.182 & 0.185 & 0.153 & 0.147 &   &   & 0.067 & 0.02 & 0.963 & 0.465 & 0.658 & 0.323\\

@@

Single/multiple & \(\Pi\) & 1.738 & 1.919 & 0.668 & 0.82 & 0.094 & 0.087 & 0.134 & 0.254 & 1.228 & 0.779 & 0.125 & 0.258\\
source candidate & \(\Lambda\) & 1.678 & 1.723 & 0.291 & 0.292 & 0.234 & 0.239 & 0.099 & 0.153 & 1.005 & 0.554 & 0.257 & 0.613\\
\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(\Delta \Lambda\) & 0.182 & 0.197 & 0.157 & 0.145 &   &   & 0.067 & 0.097 & 0.927 & 0.544 & 0.439 & 0.379\\

@@

With/without & \(\Pi\) & 1.749 & 1.796 & 0.545 & 0.753 & 0.099 & 0.09 & -0.039 & 0.065 & 1.382 & 0.882 & 0.688 & 0.233\\
\SI{8}{\um} emission & \(\Lambda\) & 1.687 & 1.691 & 0.298 & 0.29 & 0.222 & 0.238 & 0.012 & 0.014 & 0.973 & 0.91 & 0.9 & 0.89\\
\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(\Delta \Lambda\) & 0.198 & 0.183 & 0.193 & 0.142 &   &   & 0.028 & -0.098 & 0.738 & 0.771 & 0.772 & 0.226\\
3-star vs (4+5)-star & \(\Pi\) & 1.615 & 2.026 & 0.618 & 0.773 & 0.108 & 0.07 & \bfseries 0.39 & \bfseries 0.599 & 1.25 & \bfseries 0.000411 & \bfseries 5.64e-07 & 0.128\\
 & \(\Lambda\) & 1.621 & 1.787 & 0.276 & 0.286 & 0.244 & 0.223 & \bfseries 0.369 & \bfseries 0.592 & 1.036 & \bfseries 0.000183 & \bfseries 2.24e-06 & 0.852\\
\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(\Delta \Lambda\) & 0.183 & 0.189 & 0.153 & 0.156 &   &   & -0.0 & 0.039 & 1.017 & 0.479 & 0.999 & 0.4\\

@@

MIPS vs Orion & \(\Pi\) & 1.787 & 3.09 & 0.716 & 1.666 &   &   & \bfseries 0.557 & \bfseries 1.581 & \bfseries 2.325 & \bfseries 0.000456 & \bfseries 8.48e-05 & \bfseries 2.42e-05\\
 & \(\Lambda\) & 1.69 & 2.532 & 0.292 & 0.749 &   &   & \bfseries 0.735 & \bfseries 2.428 & \bfseries 2.568 & \bfseries 4.28e-06 & \bfseries 2.13e-07 & \bfseries 1.26e-08\\
\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(\Delta \Lambda\) & 0.186 & 0.329 & 0.154 & 0.257 &   &   & \itshape 0.349 & \itshape 0.874 & \itshape 1.666 & \itshape 0.0185 & \itshape 0.0137 & \itshape 0.0199\\

@@

MIPS vs RSG & \(\Pi\) & 1.787 & 1.479 & 0.716 & 0.227 &   &   & -0.238 & -0.443 & \itshape 0.317 & \bfseries 0.0011 & 0.112 & \itshape 0.0108\\
 & \(\Lambda\) & 1.69 & 1.41 & 0.292 & 0.101 &   &   & \bfseries -0.648 & \bfseries -0.99 & \itshape 0.345 & \bfseries 2.19e-05 & \bfseries 1.5e-05 & \itshape 0.00549\\
\(n_{\text{A}}, n_{\text{B}} = 227, 16\) & \(\Delta \Lambda\) & 0.186 & 0.073 & 0.154 & 0.038 &   &   & \itshape -0.442 & \itshape -0.743 & \itshape 0.246 & \itshape 0.013 & \itshape 0.0181 & \itshape 0.00698
